\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
cite typo

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes.
However, choosing alternative moves (by changing lanes or rerouting) is an
important constituent of a sufficient condition for the liveness of a road
network cite{AAAI11-au}.

>>>>

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes.
However, choosing alternative moves (by changing lanes or rerouting) is an
important constituent of a sufficient condition for the liveness of a road
network \cite{AAAI11-au}.
